Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
AWS GPU subseccioniniciado

\subsubsection{GPUs}

>>>>

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
bandwidthtest. As it is shown in the Table~\ref{}, as the bandwidth achieved 
in this test is higher than the network bandwith, it reveals that it is a 
real GPU.
